---
title: "sustainability_group3 - Trees"
output: html_document
date: "2023-02-06"
author: "Fabian Lüthard, Elisabeth Freimann, Simon Kohler"
output:
  html_document:
    df_print: paged
    toc: yes
    theme: united
    number_sections: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Title

## Goal of the project:
Does the planting of trees and the development of areas of green spaces have a positive correlation with the development of air quality indicators in the city of Zurich?
More specific questions after exploratory analysis.


## Importing all packages and libraries

The following libraries were used to analyse the data:

```{r lib, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(tseries)
library(astsa)
library(imputeTS)
library(forecast)
library(magrittr)
library(dplyr)
library(lubridate)
library(tidyr)  
library(ggplot2)
library(reshape2) 
```

## Loading the data

```{r trees, echo=TRUE}
d.trees <- read.csv('../datasets/gsz.baumkataster_baumstandorte.csv')
head(d.trees)
str(d.trees)

```

```{r temp, echo=TRUE}
filenames.meteo <- list.files(path = "../datasets/meteo/", pattern = "*.csv", full.names = TRUE)
data_list.meteo <- lapply(filenames.meteo, read.csv)
# Combine the data frames in the list into a single data frame
meteo <- do.call(rbind, data_list.meteo)

names(meteo)[1] <- "Date"

meteo <- meteo[meteo$Standort=="Zch_Stampfenbachstrasse",]
meteo <- meteo %>% 
  select(c("Date","Parameter","Wert")) %>%
  pivot_wider(id_cols = "Date",names_from = "Parameter",values_from = "Wert") %>%
  select(c("Date","T","RainDur","p"))

meteo$Date <- format(as.Date(meteo$Date), format = "%Y-%m-%d")
meteo$Date <- ymd(meteo$Date)


head(meteo)
```

```{r air, echo=TRUE}

filenames.air <- list.files(path = "../datasets/air/", pattern = "*.csv", full.names = TRUE)
data_list.air <- lapply(filenames.air, read.csv)
# Combine the data frames in the list into a single data frame
air <- do.call(rbind, data_list.air)
names(air)[1] <- "Date"
air$Date <- as.Date(format(air$Date), "%Y-%m-%d")

air <- air[air$Standort=="Zch_Stampfenbachstrasse",]

air <- air %>% 
  select(c("Date", "Parameter", "Wert")) %>%
  pivot_wider(id_cols = "Date",names_from = "Parameter",values_from = "Wert") 

keep <- c("Date", "CO", "NOx")
air <- air[keep]
keep <- c("Date", "CO")
air.co2 <- air[keep]
keep <- c("Date", "NOx")
air.NOx <- air[keep]
#air.NOx <- air["NOx"] <- log(air["NOx"])

```


## Getting an overview about the dataset

```{r plot_air, echo=TRUE}

#melt data frame into long format
air.plot <- melt(air.co2,  id.vars = "Date")
#create line plot for each column in data frame
ggplot(air.plot, aes(Date, value), group = 5) +
  geom_line(aes(colour = variable))

```

## Timeseries Analysis
```{r time_meteo, echo=TRUE}

meteo %<>% complete(Date=seq.Date(min(Date), max(Date), by='day'))

# Use the time series class of the library stats
freq_daily <- 365.2422
temp <-
  ts(meteo$T, start=c(year(min(meteo$Date)),yday(min(meteo$Date))),
     frequency=freq_daily) %>%
  na_replace(fill=0)

# Stationarity test and decomposition
adf.test(temp,k=0)
temp_comp=decompose(temp)
plot(temp_comp)
title(sub = "Temperature")

# Manual decomposition
meteo %<>% mutate(year=year(meteo$Date)+yday(meteo$Date)/freq_daily)
temp_trend <- lm(meteo$T~meteo$year)
plot(temp, main="Temperature trend per year")
abline(temp_trend)


# Yearly and monthly data are already prepared

meteo_yr <- meteo %>%
  mutate(temp_raw=replace_na(T,0)) %>%
  group_by(Year=year(Date)) %>%
  filter(Year>=2010 & Year<=2021) %>%
  summarize(temp=mean(temp_raw)) %>%
  ungroup()


temp_yr <- ts(meteo_yr$temp, start=min(meteo_yr$Year), frequency=1)

```


```{r time_air, echo=TRUE}

air %<>% complete(Date=seq.Date(min(Date), max(Date), by='day'))

# Use the time series class of the library stats
freq_daily <- 365.2422
co2 <-
  ts(air$CO, start=c(year(min(air$Date)),yday(min(air$Date))),
     frequency=freq_daily) %>%
  na_replace(fill=0)
NOx <-
  ts(air$NOx, start=c(year(min(air$Date)), yday(min(air$Date))),
     frequency=freq_daily) %>%
  na_replace(fill=0)

# Stationarity test and decomposition
adf.test(co2,k=0)
adf.test(NOx,k=0)
co2_comp=decompose(co2)
NOx_comp=decompose(NOx)
plot(co2_comp)
title(sub = "CO2")
plot(NOx_comp)
title(sub = "NOx")


# Manual decomposition
air %<>% mutate(year=year(air$Date)+yday(air$Date)/freq_daily)
co2_trend <- lm(air$CO~air$year)
NOx_trend <- lm(air$NOx~air$year)
plot(co2, main="CO2 trend per year")
abline(co2_trend)
plot(NOx, main="NOx trend per year")
abline(NOx_trend)

air_yr <- air %>%
  mutate(co2_raw=replace_na(CO,0), NOx_raw=replace_na(NOx,0)) %>%
  group_by(Year=year(Date)) %>%
  filter(Year>=2010 & Year<=2021) %>%
  summarize(co2=sum(co2_raw), NOx=mean(NOx_raw)) %>%
  ungroup()

# Time series
co2_yr <- ts(air_yr$co2, start=min(air_yr$Year), frequency=1)
NOx_yr <- ts(air_yr$NOx, start=min(air_yr$Year), frequency=1)

par(mfrow=c(1,1))
plot(co2_yr)
plot(NOx_yr)

# Manual decomposition
co2_yr_trend <- lm(air_yr$co2~air_yr$Year)
plot(co2_yr, xlab='Year', ylab='Average co2 pollution')
abline(co2_yr_trend)


plot(co2_yr)
pacf(co2_yr)
plot(tbats(co2_yr)) # Why not decompose()?
plot(residuals(tbats(co2_yr)))
adf.test(co2_yr)

# Do not use "out of the box" except for exploration
plot(forecast(co2_yr))
```
